Checkpoint 4

### 2020-04-29 Checkpoint 4.Rmd
Update Checkpoint 4.Rmd
Added Models: Black, Pct Neg

>>>>

# Will's Models

-Variables of Interest:
*Pct Black
*Pct Positive
*Pct Negative

```{r}
mod_data<-Finaldata%>%
  mutate(Date = as.numeric(Day))%>%
  mutate(positive_rate = positive/ totalTestResults)%>%
  mutate(negative_rate = 1-positive_rate) %>% 
  select(State, ChinaVirusInterest, Day, percent_white, percent_black, positive_rate, negative_rate, KungFluInterest, Region, StateColor)
model_data<- na.omit(model_data)
```

```{r}
set.seed(454)
#Neg Rate
model_14 <- stan_glmer(
  ChinaVirusInterest ~ Day + (1 | State) + negative_rate,
  data = mod_data, family = gaussian, chains = 4, iter = 1000
)
```

```{r}
head(data.frame(summary(model_14)),-2)
```

```{r}
# Store the chains
model_14_df <- as.array(model_14) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_14_df <- model_14_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_14_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
```

```{r}
model_15<-stan_glmer(
  ChinaVirusInterest ~ (Day|State) + negative_rate, 
  data=mod_data, family=gaussian, chains =4, iter = 5000
)
```

```{r}
head(data.frame(summary(model_15)),-2)
```

```{r}
# Store the chains
model_15_df <- as.array(model_15) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_15_df <- model_15_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_15_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
```

```{r}
model_16<-stan_glmer(
  ChinaVirusInterest~ (1|State) + percent_black + negative_rate, 
  data = mod_data, family = gaussian, chains = 4, iter = 5000
)
```

```{r}
head(data.frame(summary(model_16)),-2)
```

```{r}
# Store the chains
model_16_df <- as.array(model_16) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_16_df <- model_16_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_16_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
```

```{r}
# Pct black, Neg Rate: Random effects
model_17<-stan_glmer(
  ChinaVirusInterest~ (Day|State) + percent_black + negative_rate, 
  data = mod_data, family = gaussian, chains = 4, iter = 2*5000
)
```

```{r}
head(data.frame(summary(model_17)),-2)
```

```{r}
model_17_df <- as.array(model_17) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_17_df <- model_17_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_17_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
```
